%% start of file `template.tex'.
%% Copyright 2006-2013 Xavier Danaux (xdanaux@gmail.com).
%
% This work may be distributed and/or modified under the
% conditions of the LaTeX Project Public License version 1.3c,
% available at http://www.latex-project.org/lppl/.


\documentclass[10pt,a4paper]{moderncv}        

% modern themes
\moderncvstyle{banking}                            
\moderncvcolor{black}                               

\usepackage[utf8]{inputenc}                      
\nopagenumbers            
\def\labelitemi{$\bullet$}
% adjust the page margins
\usepackage[bottom=0.5in,top=0.5in,scale=0.80]{geometry}
\usepackage{multicol}

\usepackage{import}
\usepackage{amsmath}
\usepackage{fontawesome} %% for symbols
% personal data
\name{\Large{Curriculum Vitae---Dr. Charlotte}}{\Large{M. Jones-Todd}}

%----------------------------------------------------------------------------------
%            content
%----------------------------------------------------------------------------------
\begin{document}

\makecvtitle
\vspace{-30pt}

\section{Personal Details}

\vspace{2pt}

\textbf{Position:} Lecturer\\
%% \textbf{Phone:}\\
\textbf{Address:} 303.318, Department of Statistics, University of Auckland, Auckland 1142, New Zealand\\
%% \textbf{Visa:} British Citizen; Full NZ Work Visa\\
\textbf{Email:} \href{mailto:c.jonestodd@auckland.ac.nz}{c.jonestodd@auckland.ac.nz}\\
\textbf{Online:} \faGithub \hspace{1pt} \httplink{github.com/cmjt}\hspace{4pt} \faTwitter \hspace{1pt} @cmjonestodd \hspace{1pt} @statbiscuit \hspace{4pt} \faDesktop \hspace{1pt} \httplink{cmjt.github.io}

%%\httplink{publons.com/author/1320569/charlotte-jones-todd}



\vspace{2pt}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%5
\section{Education}

\vspace{2pt}

\begin{itemize}

\item{\cventry{2013--2017}{University of St Andrews}{PhD in statistics}{Scotland, UK}{}{}}

\item{\cventry{2012--2013}{University of St Andrews}{MSc in statistics \textit{dissertation distinction}}{Scotland, UK}{}{}}  % arguments 3 to 6 can be left empty

\item{\cventry{2009--2012}{Aberystwyth University}{BSc (Hons) in mathematics \textit{first class}}{Wales, UK}{}{}}  % arguments 3 to 6 can be left empty

\end{itemize}

\vspace{2pt}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%5
\section{Employment}

\vspace{6pt}

\begin{itemize}
  \item{\cventry{07/2019--present}{Senior Lecturer}{Department of Statistics, University of Auckland}{Auckland, NZ}{}{}}
  \item{\cventry{01/2018--07/2019}{Statistician}{National Institute of Water and Atmospheric Research}{Hamilton, NZ}{}{}}
   \item{\cventry{02/2017--12/2017}{Consultant}{University of St Andrews}{Scotland, UK}{\textit{School of Mathematics and Statistics \& Sea Mammal Research Unit}}{}}
\item{\cventry{02/2017--05/2017}{Consultant}{University of Auckland}{Auckland, NZ}{\textit{School of Epidemiology \& Biostatistics}}{}}
\item{\cventry{2014--2016}{Tutor}{University of St Andrews}{Scotland, UK}{\textit{School of Mathematics and Statistics \& CAPOD}}{}}
%% \item{\cventry{2014--2016}{Tutor}{University of St Andrews}{Scotland, UK}{\textit{Centre for Academic, Professional and Organisational Development }}{}}
%% \item{\cventry{2007--2012}{Veterinary Assistant}{John Downes Veterinary Surgery}{Wales, UK}{\textit{Receptionist}}{}}

\end{itemize}


\vspace{2pt}
%--------------------------------------
\section{Scholarships and Awards}
\vspace{2pt}
\begin{itemize}
\item {\cventry{2021}{New Zealand Statistical Association} {Worsley Early Career Award}{}{}{}}
  \item {\cventry{2017}{Royal Statistical Society}{Statistical Excellence Award for Early-Career Writing---Finalist}{}{}{}}
  \item {\cventry{2015}{Royal Statistical Society}{RSS 2015 Challenge---Finalist}{}{}{}}
 \item {\cventry{2013--2016}{University of St Andrews}{School of Mathematics and Statistics PhD Scholarship}{}{}{}}
 \item{\cventry{2012}{University of St Andrews}{EPSRC MSc Scholarship}{}{}{}}
   \item{\cventry{2012}{Aberystwyth University}{Pennington Prize for Pure Mathematics}{}{one per cohort}{}}
  \vspace{2pt}

\end{itemize}
  %-----------------------------------------------
  \section{Publications}

  \textit{\small{Published}} {\footnotesize${}^\ast$ Publications in journals ranked as A${}^\ast\,/\,$A (top 5$\%\,/\,$20$\%$) by the Australian Research Council}\\

  ${}^\ast$ Hin, V., de Roos, A. M., Benoit-Bird, K. J., Claridge, D. E.,
DiMarzio, N.,  Durban, J. W., Falcone, E. A., Jacobson, E. A., \textbf{Jones-Todd, C. M.}, Pirotta, E., Schorr G.S., Thomas, L., Watwood, S., \& Harwood, J.  \textbf{(In press)} Using individual-based bioenergetic models to predict the aggregate effects of disturbance on populations: a case study with beaked whales and Navy sonar. PLOS One.\\
  
  \textbf{Jones-Todd, C. M.}, Pirotta, E., Durban, J., Claridge, D., Baird, R., Falcone, E., Schorr, G., Watwood,S., \& Thomas, L.  \textbf{(2022)} Continuous-time discrete-space models of marine mammal exposure to Navy sonar. Ecological Applications, 32 (1): e02475.\\
 
  ${}^\ast$ Semadeni-Davies, A., \textbf{Jones-Todd, C. M.},  Elliott, A., Shankar, U., Tanner, C., Srinivasan, MS., \& Muirhead , R. (2020) CLUES model calibration and its implications for estimating contaminant attenuation. Agricultural Water Management, 228, 105853.\\

    Semadeni-Davies, A., \textbf{Jones-Todd, C. M.}, Srinivasan, MS.,  Muirhead , R.,  Elliott, A., Shankar, U., \& Tanner, C. (2020) CLUES model calibration: residual analysis to investigate potential sources of model error. New Zealand Journal of Agricultural Research, 1--24.\\

${}^\ast$ Soranio-Redondo, A., \textbf{Jones-Todd, C. M.}, Bearhop, S., Hilton, G. M., Lock, L., Stanbury, A., Votier, S. C., \& Illian, J. B. (2019) Understanding species distribution in dynamic populations: a new approach using spatio-temporal point process models. \textit{Ecography}, 42 (6), 1092--1102.\\
  
\vspace{-3pt}
${}^\ast$ \textbf{Jones-Todd, C. M.}, Caie, P., Illian, J. B., Stevenson, B. C., Savage, A., Harrison D, J., \& Bown, J. (2019) Identifying prognostic structural features in tissue sections of colon cancer patients using point pattern analysis. \textit{Statistics in Medicine}, 38 (8), 1421--1441.\\

\vspace{-3pt}
${}^\ast$ Python, A.,  Illian, J. B., \textbf{Jones-Todd, C. M.}, \& Bl\'{a}ngiardo, M. A Bayesian approach to modelling subnational spatial dynamics of worldwide non-state terrorism, 2010--2016. (2019) \textit{Journal of the Royal Statistical Society, Series  A (Statistics in Society)}, 182 (1), 323--344.\\

\vspace{-3pt}
Kool, B., Buller, S., Kuriyan, R., \textbf{Jones-Todd, C. M.}, Newcombe, D., \& Jones, P. (2018) Alcohol and injury among attendees at a busy inner city New Zealand emergency department. \textit{Injury}, 49 (4), 798--805.\\


  ${}^\ast$ \textbf{Jones-Todd, C. M.}, Swallow, B., Illian, J. B., \& Toms, M. (2018) A spatio-temporal multi-species model of a semi-continuous response. \textit{Journal of the Royal Statistical Society, Series C (Applied Statistics)}, 67 (3), 705--722.\\

\vspace{-3pt}
Python, A.,  Illian, J. B., \textbf{Jones-Todd, C. M.}, \& Bl\'{a}ngiardo, M. (2016) Explaining the lethality of Boko Haram’s terrorist attacks in Nigeria, 2009-2014: A hierarchical Bayesian approach. \textit{Bayesian Statistics in Action: BAYSM 2016}, 231--239.\\


\textit{\small{Under review after revision}}\\


%% \textit{\small{In preparation}}\\

%% \vspace{-3pt}

%% \textbf{Jones-Todd, C. M.}, Illian, J. B., \& Marques, T. A. Applications of a joint marked point process spatio-temporal model. In preparation for submission to \textit{Spatial Statistics}.\\
%% \vspace{5pt}

%% \vspace{-3pt}
%% Stevenson, B. C., Borchers, D. L., \textbf{Jones-Todd, C. M.}, \& Kidney, D. ascr: an R package for the analysis of spatial capture-recapture data. In preparation for submission to \textit{Ecography}.\\
%% \vspace{5pt}

%% \vspace{-3pt}

%% 

%% \subsection{Other reports}

\vspace{5pt}

\underline{\textbf{Magazine Articles}}\\

\vspace{-3pt}

Python, A.,  Illian, J. B., \textbf{Jones-Todd, C. M.}, \& Bl\'{a}ngiardo, M. (2019) The Deadly Facets of Terrorism. \textit{Significance}, 16 (4), 28--31.\\

\vspace{-3pt}

\textbf{Jones-Todd, C. M.} A time to kill: Great British serial killers. \textit{Significance}. December 2017. \url{https://www.significancemagazine.com/culture/577-a-time-to-kill-great-british-serial-killers}\\

\vspace{2pt} 

\underline{\textbf{Reports}}\\

Hatami, R., Lane, S., Robinson, A.,  Inglis, G.,  \textbf{Jones-Todd, C. M.}, \& Seaward, K. Improving New Zealand’s marine biosecurity surveillance programme. A statistical review of biosecurity vectors.  Ministry for Primary Industries website. January 2021.\\

\vspace{-3pt}

Python, A.,  Illian, J. B., \textbf{Jones-Todd, C. M.}, \& Bl\'{a}ngiardo, M. Statistics and Terrorism: Insights on terrorism lethality from Bayesian modeling. \textit{Wiley StatsRef-Statistics Reference Online}. July 2020.\\

Dudley, B., \& \textbf{Jones-Todd, C. M.} New Zealand coastal water quality assessment update. Ministry for the Environment. May 2018.\\

\vspace{-3pt}

Graham, E., \textbf{Jones-Todd, C. M.}, Wadhwa, S., \& Storey, R. Analysis of stream responses to riparian management on the Taranaki ring plain. Taranaki Regional Council. March 2018.\\

\vspace{2pt}

\underline{\textbf{\texttt{R} packages}}\\
\vspace{-3pt}

Jones-Todd C, van Helsdingen A (2022). \texttt{stelfi}: Hawkes and Log-Gaussian Cox Point Processes Using Template Model Builder. \texttt{R} package version 0.0.1, \url{https://github.com/cmjt/stelfi/}.\\

\vspace{-3pt}

\texttt{mmre}. Package to fit two-stare continuous-time discrete-space Markov models with individual level random effects, \url{https://github.com/cmjt/mmre}.\\

\vspace{-3pt}

\texttt{lgcpSPDE}. Package to fit and simulate log-Gaussian Cox point processes using the INLA-SPDE approach, \url{https://github.com/cmjt/lgcpSPDE}.\\

\vspace{2pt}

\underline{\textbf{\texttt{RShiny} applications}}\\
\vspace{-3pt}

\texttt{vested}. Implements the setting up of \texttt{v}irtual \texttt{e}xperiment\texttt{s} to \texttt{t}each \texttt{e}xperimental \texttt{d}esign, \url{https://cmjt.shinyapps.io/vested/}.\\

\vspace{-3pt}

\texttt{penguin}. Introduces linear modelling using the \texttt{palmerpenguins} data, \url{https://cmjt.shinyapps.io/penguin/}.\\

\vspace{-3pt}

\texttt{ascr\_shiny}. Interface for the \texttt{R} package \texttt{ascr}, which fits SCR models to estimate animal density from acoustic surveys, \url{https://cmjt.shinyapps.io/ascr_shiny/}.\\

\vspace{-3pt}

\texttt{probable}. Explores distributions and visualises the CLT in action, \url{https://cmjt.shinyapps.io/probable/}.\\



%\newpage

%-----------------------------------------------
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Service}
\vspace{6pt}

\begin{itemize}
  
  \item Chair for the Student Sustainability Awards, 2022 \& 2023
  \item ''Tips for Academic talks'' PhD student panel, Dept. of Statistics
  \item Judging panel chair for the 2021 PhD talks day, Dept. of Statistics
  \item Panel member for the Student Sustainability Awards, 2021
  \item Contributor to the New Zealand Statistical Association's 2021 Q1 newsletter
  \item Technical support for the Statistics Teachers' Day, 2020 \textit{Bring Your Own `big ideas' for teaching statistics}
\item Member of the International Statistical Ecology Conference (ISEC) 2020 local organising committee.
\item Department of Statistics, University of Auckland
  \begin{itemize}
  \item \textit{Social Media officer}
  \item \textit{Chair of the Christmas function organising committee, 2020}
  \item \textit{Department of Statistics working from home committee}
  \item \textit{Department of Statistics sustainability working group coordinator}
  \item \textit{Member of the Faculty of Science sustainability committee}
  \item \textit{Ecological statistics group coordinator}
  \end{itemize}
\item Judge at the Waikato Science and Technology Fair 2018
\end{itemize}



%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Other Service}

\vspace{6pt}

\begin{itemize}
\item \textbf{Associate Editor}
  \begin{itemize}
  \item \textit{Journal of Statistical Theory and Practice}
  \end{itemize}
\item \textbf{Conference session chair}
  \begin{itemize}
  \item virtual Australia and New Zealand Statistical Conference (vANZSC), July 2021.
  \item virtual National Centre for Statistical Ecology v(NCSE), June 2021.
  \item virtual International Statistical Ecology Conference (vISEC), July 2020.
  \item Statistics in Ecology and Environmental Monitoring (SEEM) Conference, December 2019.
  \end{itemize}
\item \textbf{Student paper judge}
  \begin{itemize}
  \item virtual Australia and New Zealand Statistical Conference (vANZSC), July 2021.
  \item virtual International Statistical Ecology Conference (vISEC), July 2020.
  \end{itemize}
\item \textbf{Manuscript reviewing}
  \begin{itemize}
  \item \textit{Methods in Ecology and Evolution}
  \item \textit{Spatial Statistics}
  \item \textit{Journal of Peace Research}
  \item \textit{Advances in Statistical Analysis}
  \item   \textit{Scientific Reports}
  \item \textit{Ecology}
  \item  \textit{Journal of the Royal Statistical Society, Series C}
  \item   \textit{Ecology and Evolution}
  \item   \textit{Ecological Research}
  \end{itemize}
\item \textbf{Interview panel member}\\
  Centre for Academic, Professional and Organisational Development (CAPOD).
\end{itemize}




%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newpage
\section{Grants \& Contracts}

\vspace{6pt}
\begin{itemize}
\item 2022
  \begin{itemize}
  \item Marsden Fund Fast-Start Grant, Royal Society of New Zealand (\$360,000)
  \item Teaching Development Fund, Faculty of Science, University of Auckland (\$5,000)
  \end{itemize}
\item 2021
  \begin{itemize}
  \item Impact Strategic Fund, Faculty of Science, University of Auckland (\$5,000)
  \item Asian Office of Aerospace Research and Development (\$70,000)
  \item Teaching Development Fund, Faculty of Science, University of Auckland (\$5,000)
  \end{itemize}
\item 2020
  \begin{itemize}
  \item Faculty Research Development Fund, Faculty of Science, University of Auckland (\$20,000)
  \item National Institute of Water and Atmospheric Research contract (\$10,000)
  \end{itemize}
\end{itemize}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Students}

\vspace{6pt}

\begin{itemize}
\item Honours \& Masters
  \begin{itemize}
  \item Chuyang Huang \& Guoxiang Yu MProfStuds in Data Science, \textit{Gamification of statistical theory}, 2021
  \item Haiyi Shi, honours \textit{The role of the 'mesh' when using INLA to fit point process models}, 2021
  \item Alice Hankin, honours \textit{Modelling terrorism incidents as a log-Gaussian Cox process}, 2021
  \item Jenny Pullan, MSc \textit{RShiny application to aid in the calculation of site-adjusted water quality guidelines}, 2021.
  \item Zhenyuan Zhang, MProfStuds in Data Science \textit{Data scraping and wrangling}, 2021.
  \item Elvyna Tunggawan, MProfStuds in Data Science \textit{Analyzing activity data from rheumatoid arthritis patients}, 2020.
  \item Anthony Timings (Charlie), honours \textit{Spatiotemporal modelling of NZ murders}, 2020.
  \end{itemize}
\item PhD
  \begin{itemize}
  \item Alec van Helsdingen, \textit{Modelling Self-Excitement Inherent in Spatial and Spatio-Temporal Point Pattern Data}, 2022--ongoing.
   \item Deborah Kakis, \textit{Investigating Statistical Literacy among Health Care Professionals in Papua New Guinea}, 2023--ongoing.
  \end{itemize}
\end{itemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Technical Skills}

\vspace{6pt}
\textbf{Advanced user of:} R, Git, Bash, \LaTeX, C++, HTML, CSS, Python

\section{Memberships}

\vspace{6pt}
\begin{itemize}
\item New Zealand Statistical Association (NZSA)
\item International Biometric Society (IBS), Australasian Region
\end{itemize}
%-----       letter       ---------------------------------------------------------

\end{document}
